Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-13 ms.tex
updated model figure, other small changes

@@

Following Luce's choice axiom \cite{Luce1959}, an agent using asocial information selects a behavior at random, with the probability of selecting any particular behavior weighted by the softmax function applied to that behavior's observed mean payoff relative to all 
mean payoffs: 
$\Pr(\text{choose behavior }b) = 
  \frac{\exp(\bar\pi_b / \tau) }{ 
\sum_{b=1}^B \exp(\bar\pi_b / \tau)}$.
The softmax method is a biologically plausible model~\cite{Schulz2019} that enables agents to explore alternative behaviors sometimes and exploit the best observed behavior other times.  The parameter $\tau$ specifies
how frequently alternative behaviors are explored---higher $\tau$ means more
frequent exploration. We set $\tau = 0.1$ for all computational analyses 
presented in the main paper. We (WILL) perform(ED) sensitivity analyses 
and found a weak dependence on $\tau$ that does not affect our main conclusions.

@@

  \item 
    Our analysis confirmed existing theoretical predictions that social learning
    is valuable only when environmental variability $u$ is sufficiently small.
    Because of the central role of $u$, it is set on the x-axis in
    all plots shown in Figure~\ref{fig:results}. 
    The threshold at which social learning stops being strongly selected for
    varies depending on the value of other environmental parameters.

  \item 
    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
    third column respectively in Figure~\ref{fig:results}) can lead
    social learning to be selected for even for large values of $u$, possibly
    due to the low risk and potentially high reward of learning an accurate
    tally of mean payoffs from the previous generation. 
    Since there are so many behaviors and so
    few observations, softmax weighting will not significantly 
    favor a sub-optimal behavior. However, if one does learn an accurate tally
    then one does have an increased chance of performing the best one.
    \begin{itemize}
      \item 
        (THIS MAKES SENSE, BUT THE EFFECT IS TOO STRONG. WHY SHOULD THERE BE ANY
        SOCIAL LEARNING WHEN U = 1.0?  I THINK SOMETHING IS SLIGHTLY WRONG WITH THE
        MODEL---I'M WORKING ON CHECKING WHAT THAT MIGHT BE)
      \item
        ONE THING TO CHECK IS THE FRACTION DOING THE OPTIMAL BEHAVIOR WHEN
        $u=1$. IF MANY START OUT DOING OPTIMAL, THEN SOMETHING MAY BE WRONG.
    \end{itemize}

>>>>

% Colored comments 
\usepackage{color}
\definecolor{myorange}{RGB}{240, 96, 0}
\newcommand{\mt}[1]{{\textcolor{myorange} {({\tiny MT:} #1)}}}

\definecolor{myblue}{RGB}{30,144,255}
\newcommand{\jhj}[1]{{\textcolor{myblue} {({\tiny JHJ:} #1)}}}

\definecolor{mypurple}{RGB}{148,0,211}
\newcommand{\cm}[1]{{\textcolor{mypurple} {({\tiny CM:} #1)}}}

\definecolor{mygreen}{RGB}{26, 153, 51}
\newcommand{\ps}[1]{{\textcolor{mygreen} {({\tiny PS:} #1)}}}

@@

Following Luce's choice axiom \cite{Luce1959}, an agent using asocial information selects a behavior at random, with the probability of selecting any particular behavior weighted by the softmax function applied to that behavior's observed mean payoff relative to all 
mean payoffs: 
$\Pr(\text{choose behavior }b) = 
  \frac{\exp(\bar\pi_b / \tau) }{ 
\sum_{b=1}^B \exp(\bar\pi_b / \tau)}$.
The softmax method is a biologically plausible model~\cite{Schulz2019} that enables agents to explore alternative behaviors sometimes and exploit the best observed behavior other times.  The parameter $\tau$ specifies
how frequently alternative behaviors are explored---higher $\tau$ means more
frequent exploration. We set $\tau = 0.1$ for all computational analyses 
presented in the main paper. We (WILL HAVE) performed sensitivity analyses 
and found a weak dependence on $\tau$ that does not affect our main conclusions.

@@

  \item 
    Our analysis confirmed existing theoretical predictions that social learning
    is valuable only when environments are sufficiently stable, i.e., 
    environmental variability $u$ is sufficiently small.
    Because of the central role of $u$, it is set on the x-axis in
    all analysis plots shown in Figure~\ref{fig:results}. 
    The threshold over $u$ at which social learning begins to decline
    varies depending on the value of other environmental parameters.

  \item 
    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
    third column respectively in Figure~\ref{fig:results}) can lead
    social learning to be selected for even for large values of $u$, possibly
    due to the low risk and potentially high reward of learning an accurate
    tally of mean payoffs from the previous generation. 
    Since there are so many behaviors and so
    few observations, softmax weighting will not significantly 
    favor a sub-optimal behavior. However, if one does learn an accurate tally
    then one does have an increased chance of performing the best one.
    \begin{itemize}
      \item 
        \mt{This makes sense, but the effect is too strong. Why should there be any
        social learning when u = 1.0?  I think something is slightly wrong with the
        model---I'm working on checking what that might be}
      \item
        \mt{One thing to check is the fraction doing the optimal behavior when
        $u=1$. If many start out doing optimal, then something may be wrong.}
    \end{itemize}
